A gossip-based protocol for exchanging immutable data in dynamic distributed environments

### 2011-07-20 papers/paper1/paper.tex
A little progress on implentation, changed diagram one

@@

\section{Implementation}

%%TODO: Talk about validation

\paragraph{MFTP Automaton.}
Our implementation of MFTP uses the ioa framework.
I/O Automata model stateful distributed system components that can interact and be composed with each other.
They change state through transitions classified as input, output or internal actions.
Input and output actions in different automata are bound; output actions in the one trigger input actions in the other.

%%Describe our implementation at the 50k ft view and work our way down until things are no longer interesting.
We define a basic MFTP automaton, a sender, and a receiver.
The responsibilities of the MFTP automaton are to acquire data and to help others acquire it.
Each MFTP automaton begins with a file, encapsulated in a File object, which is either incomplete or complete.
If the file is incomplete, the automaton generates requests for the missing fragments.
If the file is complete, the automaton may serve the file, or it may serve the file while performing matching on it.

%%Picture of mFTP automaton?

The automaton reports that its file is complete using the download complete output action.

\paragraph{Some useful stuff.} %% We know it's rough, but what else can we do?
The sending automaton uses the UDP sender built into ioa to multicast messages one at a time.
The receiving automaton uses the ioa UDP receiver.
The sender and receiver automata may be connected to more than one MFTP automaton.

\vspace{5mm}
\includegraphics[scale=0.65]{diagramOne}

\paragraph{Jam.} %%needs different header
Our implementation defines three file types, \emph{data}, \emph{meta} and \emph{query}.  
A data file contains data from any file in the network.
A meta file contains as data the file ID of a file in the network and its name. 
A query file contains only the name of the file which is being queried.

\vspace{2 mm}

\includegraphics[scale=0.55]{share_diagram}

\vspace{2 mm}

\vspace{2.5 mm}

\includegraphics[scale=0.65]{get_diagram}

\vspace{2 mm}

%%\begin{itemize}
%%  \item Problem
%%  \item Design forces
%%  \item Solution
%%  \item Consequences
%%\end{itemize}

\section{Evaluation and Discussion\label{evaluation}}

\begin{itemize}
\item Translation of automaton in \emph{Distributed Algorithms} to C++.
\item Simulate a protocol then replace with network components
\item Compare a protocol using: single-threaded event-based (select loop), multi-threaded, I/O automata
\item Show a buggy program and then apply an invariant to find the bug.
\end{itemize}

Bring up style mentioned in section \ref{representation}.

\section{Related Work\label{related_work}}

pthreads (?)
Edward Lee - The Problem with Threads
Herb Sutter - The Free Lunch is Over
Early work on concurrency

\section{Conclusion and Future Work\label{conclusion}}

\begin{itemize}
  \item We are going to use it to build the substrate.
  \item Speculate on moving down into operating system (device drivers would be easy, IPC including filesystem replaced by automata)
  \item Speculate on moving down into the hardware level (Local talent, Ivan Sutherland)
  \item We can take advantage of multi-core in a very straight-forward way
  \item New problems in scheduling (Pinning automata to processors to minimize actions that span two processors.  Maximum independent set.)
  \item We are non-blocking all the way.  Combine this with a deterministic implementation of the scheduler and model and there are serious opportunities for real-time.
\end{itemize}

>>>>

\section{Design}
%% General stuff -- The short argument is we're developing a new protocol
%% the I/O Automata formal model is good for modeling protocols, therefore we modeled it as an mftp automaton
%% Diagram with the 3 pieces
%% Describe the diagram, this is how we're going to do it, this is how we're interfaced and kinda put things together
%% then go into MFTP Automaton, state, etc
%% then go on and talk about the actions (send receive etc)

The I/O Automata formal model is a well-established technique for building protocols.
%% Talk about why I/O Automata is a good method (even though we didn't have a choice)
I/O Automata model stateful distributed system components that can interact and be composed with each other.
They change state through transitions classified as input, output or internal actions.
Input and output actions in different automata are bound; output actions in the one trigger input actions in the other.
As a result, we present our design of the MFTP protocol as automata.

\begin{figure}
  \center
  \includegraphics[scale=0.65]{diagramOne}
  \caption{Basic implementational view of the protocol \label{DesignOne}}
\end{figure}

\ref{DesignOne} outlines the necessary pieces which constitute our protocol.
We define a basic MFTP automaton and a broadcast/multicast channel automaton.
We define a basic MFTP automaton, a sender, and a receiver.
The responsibilities of the MFTP automaton are to acquire data and to help others acquire it.

Each MFTP automaton begins with a file, encapsulated in a File object, which is either incomplete or complete.
If the file is incomplete, the automaton generates requests for the missing fragments.
If the file is complete, the automaton may serve the file, or it may serve the file while performing matching on it.

The broadcast/multicast channel automaton uses the UDP sender and receiver built into ioa.
The channel may be connected to more than one MFTP automaton.

The automaton reports that its file is complete using the download complete output action.
%%  to multicast messages one at a time.
%%The receiving automaton uses the ioa UDP receiver.

\section{Implementation}
%% We implimented our IO Automata design using ioa framework
%% Interesting techniques - suicide, recursive automata

\section{Evaluation and Discussion\label{evaluation}}
\paragraph{Jam.} %%needs different header
Our implementation defines three file types, \emph{data}, \emph{meta} and \emph{query}.  
A data file contains data from any file in the network.
A meta file contains as data the file ID of a file in the network and its name. 
A query file contains only the name of the file which is being queried.

\begin{figure}
  \center
  \includegraphics[scale=0.65]{share_diagram}
  \caption{The share program \label{EvaluationOne}}
\end{figure}

\begin{figure}
  \center
  \includegraphics[scale=0.65]{get_diagram}
  \caption{The get program \label{EvalutationTwo}}
\end{figure}

\section{Related Work}

\section{Conclusion}

@@
